Reanalysis Step 6: Sensitivity Analysis and E-values

### 2025-09-01 reanalysis-6-sensitivity-interaction.qmd
fix evalues
sensitivity analysis bugs

```{r setup}
#| include: false
# Setup analysis environment
source("dependencies.R")
setup_analysis(seed = 2025)

@@

# Calculate E-value for the main effect
if (or_main > 1) {
  evalue_main <- evalues.OR(
    est = or_main,
    lo = ci_lower_main,
    hi = ci_upper_main,
    rare = TRUE  # Assuming rare outcome
  )
} else {
  # If OR < 1, we need to take the reciprocal
  evalue_main <- evalues.OR(
    est = 1/or_main,
    lo = 1/ci_upper_main,
    hi = 1/ci_lower_main,
    rare = TRUE
  )
}

@@

  # Calculate E-value
  if (or_val > 1) {
    evalue <- evalues.OR(
      est = or_val,
      lo = ci_lower,
      hi = ci_upper,
      rare = TRUE
    )
  } else {
    evalue <- evalues.OR(
      est = 1/or_val,
      lo = 1/ci_upper,
      hi = 1/ci_lower,
      rare = TRUE
    )
  }

>>>>

```{r setup}
#| include: false
# Setup analysis environment
source("dependencies.R")
source("functions.R")  # Load formula definitions and helper functions
setup_analysis(seed = 2025)

@@

# Calculate E-value for the main effect
if (or_main > 1) {
  evalue_main <- evalues.OR(
    est = or_main,
    lo = ci_lower_main,
    hi = ci_upper_main,
    rare = FALSE  # VI/blindness is not rare in this population
  )
} else {
  # If OR < 1, we need to take the reciprocal
  evalue_main <- evalues.OR(
    est = 1/or_main,
    lo = 1/ci_upper_main,
    hi = 1/ci_lower_main,
    rare = FALSE
  )
}

@@

  # Calculate E-value
  if (or_val > 1) {
    evalue <- evalues.OR(
      est = or_val,
      lo = ci_lower,
      hi = ci_upper,
      rare = FALSE
    )
  } else {
    evalue <- evalues.OR(
      est = 1/or_val,
      lo = 1/ci_upper,
      hi = 1/ci_lower,
      rare = FALSE
    )
  }

### 2025-09-01 reanalysis-6-sensitivity.qmd
sensitivity analysis bugs

  # Extract lapse effect
  cc_coef <- coef(summary(cc_model))
  cc_lapse <- cc_coef["ever_lapse_binary", ]

@@

  coef_lapse <- coef(summary(model))["ever_lapse_binary", ]

@@

  coef_clean <- coef(summary(model_clean))["ever_lapse_binary", ]

>>>>

  # Extract lapse effect
  cc_coef <- coef(summary(cc_model))
  cc_lapse <- cc_coef["ever_lapse_binary1", ]

@@

@@

  coef_clean <- coef(summary(model_clean))["ever_lapse_binary1", ]
